Simulation of Tsunami impact upon Coastline

### 2016-04-10 paper/paper.tex
Minor corrections in paper text.

\paragraph{} Simulations of natural phenomena are a precious tool for analysis and
understanding of the processes behind them as well as the implications of
those. Especially fluid dynamics is one of the fields most benefitted by the explosive
growth of high performance parallel computing architectures of the last years. Tsunamis
are one of the most devastating natural disasters, with much attention drawn to them
lately, especially after the 2004 Indian Ocean tsunami and the 2011 T\={o}hoku earthquake
and tsunami, two of the largest incidents in modern history. Multiscale modelling of
tsunami generation, propagation and impact is a trending research area as respective
simulations give valuable insights into the underlying mechanisms and relations between
the various stages of an unfolding tsunami incident, while also facilitating the
assessment of potential hazard it poses upon impact on a coastline.

@@

\paragraph{} Tsunami simulations have been shown to be a valuable tool in the literature,
aiding in estimation of key parameters of a tsunami incident, such as its propagation
course and coastal inundation. Simulations of the devastating 2004 Indian Ocean tsunami
have been carried out by Wang and Liu \cite{wang2007} and Ioualalen et
al. \cite{ioualalen2007}, using nonlinear shallow water equations and nonlinear Boussinesq
models respectively. In both cases, good agreement between calculations and field
measurements of inundation and runup indicate the robustness of these approches. Samaras
et al. \cite{samaras2015} used a 2D horizontal model based on the higher oder Boussinesq
equations to simulate tsunami-induced coastal inundation in two relevant areas of interest
in the Mediterranean. Using two different models, Kakinuma \cite{kakinuma2008} reproduced
a past incident with sufficient accuracy. The governing equations for both were the
continuity and Reynolds equations for incompressible fluids in porous media, while water
surface displacement was determined by the vertically integrated continuity equation for
the first and the 3D Volume of Fluid method for the second model.

@@

\paragraph{} Due to its generality and adaptability, SPH has been the method of choice for
many applications and relative extensions. Macklin and M\"{u}ller
\cite{macklin2013position} enriched SPH with positional geometric constraints, thus
enforcing incompressibility while maintaining stability and allowing for large
timesteps. Rigid-fluid interaction is one of the strong aspects of the method, as is shown
by Akinci et al. \cite{akinci2012versatile}, where rigid surfaces are sampled by boundary
particles, which adaptively contribute to fluid properties to address boundary region
deficiencies and inhomogeneities, in order to incorporate rigid bodies to a unified
hydrodynamic framework. Finally, a thorough overview of various implementation algorithms
and data structures together with their advantages and drawbacks is provided by
Dom\'{i}nguez et al. \cite{dominguez2011}.

@@

\paragraph{} Starting from the identity:
\begin{equation*}
  f(\vec{r}) = \int_Vf(\vec{x}) \delta(\vec{r} - \vec{x}) d\vec{x},
\end{equation*}
where $\delta(\vec{r})$ the Dirac delta function and $\vec{x} \in V$, one can obtain a
more general interpolation rule by substituting $\delta(\vec{r})$ with a smoothing kernel
$W(\vec{r}, h)$:
\begin{equation*}
  \label{eq:c-approx}
  f(\vec{r}) \approx \int_V f(\vec{x}) W(\vec{r}-\vec{x}, h) d\vec{x}
\end{equation*}
whose limit when $h\to0$ approaches the delta fucntion and is normalized to unity:
\begin{equation*}
  \label{eq:kernel-properties}
  \lim_{h\to0}W(\vec{r}, h) = \delta(\vec{r})\ \ \
  \text{and}\ \ \
  \int_VW(\vec{r}, h) d\vec{x} = 1
\end{equation*}
The smoothing radius $h$ serves as a cutoff radius in the smoothing process, as particles
beyond that distance have no contribution to the sum, i.e. $W(r,h) = 0$ when $r>h$. For
the discrete case, where $f$ is discretized to particles with density $\rho$ and mass $m$,
the weighting ratio $m/\rho$ can be used to construct a weighted sum interpolant for any
field $A$:
\begin{equation}
  \label{eq:d-approx}
  A(\vec{r}) = \sum_i \frac{m_i}{\rho_i} A(\vec{r}_i) W(\vec{r}-\vec{r}_i, h)
\end{equation}
which lies at the heart of SPH formulation. According to this, the gradient can be
computed by the following approximation:
\begin{equation}
  \label{eq:d-grad}
  \nabla A(\vec{r}) = \sum_i \frac{m_i}{\rho_i} A(\vec{r}_i) \nabla W(\vec{r} - \vec{r}_i, h)
\end{equation}
The obvious advantage of this is the exclusive dependence on the smoothing kernel
gradient, which can be precomputed for sensible kernel choices. However, this formula can
lead to unsymmetric pair forces, compromising the conservation of linear and angular
momentum of the system. To symmetrize these forces depending on gradients (like those
originating from pressure differences), we can use the product rule:
\begin{equation*}
  \label{eq:grad-identity}
  \nabla \left( \frac{P}{\rho} \right) =
  \frac{\nabla P}{\rho}-
  \frac{P}{\rho^2} \nabla \rho
  \hspace{10pt} \Leftrightarrow \hspace{10pt}
  \nabla P = \rho \left[ \frac{P}{\rho^2} \nabla \rho + \nabla \left( \frac{P}{\rho}
    \right) \right]
\end{equation*}
to obtain an alternative approximation of gradient
\begin{align}
  \label{eq:grad-est}
  \nabla P & = \rho \left[ \frac{P}{\rho^2} \sum_i \frac{m_i}{\rho_i} \rho_i \nabla
             W(\vec{r}-\vec{r}_i, h)
             +
             \sum_i \frac{m_i}{\rho_i} \frac{P_i}{\rho_i} \nabla W(\vec{r}-\vec{r}_i, h)
             \right] \nonumber \\
           & = \rho \sum_i m_i \left(\frac{P}{\rho^2} + \frac{P_i}{\rho_i^2} \right)
             \nabla W(\vec{r}-\vec{r}_i, h)
\end{align}
which is antisymmetric for all interacting particle pairs. Viscosity forces on the other
hand, are proportional to the laplacian of the velocity field:
\begin{equation}
  \label{eq:lapl-est}
  \nabla^2\vec{v} = \sum_i \frac{m_i}{\rho_i} (\vec{v}_i - \vec{v}) \nabla^2
  W(\vec{r}-\vec{r}_i, h)
\end{equation}
and are always antisymmetric, since they depend on velocity difference
$\vec{v}_i - \vec{v}$ between particles.  In each timestep of the simulation, the density
of all particles is first computed according to equation (\ref{eq:d-grad}), as it depends
only on the relative position of those. The pressure at each particle location is then
obtained from its respective density through an equation of state. After this step, the
pressure and viscosity forces are computed from the particle data and integrated back into
the position and velocity of the particles.

@@

\subsubsection{Simulation initialization} Each simulation under our implementation
consists of two elements, the coastline terrain (static) and the tsunami wave
(dynamic). For the simulation setup, terrain is imported from a suitable 3D geometry
definition file format, the initial conditions of the impacting wave (position and
velocity) are configured and the desired discretization resolution for the fluid (i.e. the
number of particles it is discretized into) is set. From these conditions, the terrain and
fluid are initialized and key parameters are computed as subsequently described. Terrain
geometry is uniformly scaled by a user-supplied factor and docked to the origin of
coordinates and the particle effective radius $r$ is determined such that the specified
discretization resolution is achieved. Fluid particles are initially placed on a Hexagonal
Close-Packed lattice covering the fluid initial position, in order to accomplish the
densest possible packing and symmetry:
\begin{equation}
  \label{eq:hcp}
  [x, y, z] = \left[ 2i+[(j+k) \bmod 2], \sqrt{3}[j + \frac{1}{3} (k \bmod 2)],
    \frac{2\sqrt{6}}{3} k \right] r
\end{equation}
In this configuration, the smoothing radius $h$ is computed such that each particle has
approximately 50 neighbours (following the empirical rule established in the
literature). The timestep is calculated according to the Courant-Friedrichs-Lewy
criterion:
\begin{equation}
  \label{eq:cfl}
  \delta t_{\text{CFL}} = C \frac {\delta x}{v_{\text{max}}},
\end{equation}
for values of Courant number $C\approx0.5$ with characteristic length $\delta x$ equal to
the particle effective radius and maximum velocity $v_{\text{max}}$ determined by the
maximum potential energy in the initial configuration.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{../report/figures/lp-grid.pdf}
  \caption{Organization of the custom data structure designed for the efficient storing
    and interaction scanning between simulation particles. Top-down, the first vector
    implements the 3D to linear locality preserving mapping of cell anchors onto the
    second, which in turn points to each cell's particles on the third.}
  \label{fig:lp-grid}
\end{figure}

\subsubsection{Data organization and export} Rigid body dynamics are handled by the Bullet
physics engine. A custom cell list data structure (LP grid) was implemented in order to
optimize particle dynamic storage and access time. The simulation domain is divided by a
regular 3D grid of spacing equal to the smoothing radius into cubic cells containing the
fluid particles. Particles are generated as Bullet objects and are stored in the LP grid,
which consists of three storage vectors. As shown in Figure \ref{fig:lp-grid}, particles
are accessed by following pointers through those vectors in order. The \texttt{map} vector
contains pointers to \texttt{anchors} and in turn \texttt{anchors} pointers to
\texttt{particles}, which contains the simulation particles. Each cell's particles are
continuously stored in the \texttt{particles} vector. Each element of \texttt{anchors}
represents a cell and contains a pointer to the start of the region that contains that
cell's particles in \texttt{particles}. Since SPH access patterns are heavily reliant on
neighbour searching, increasing the locality in the linear order in which cells are stored
is clearly beneficial to performance, due to better utilization of cache memory. For that
reason, cells are represented spatially sorted along a space-filling curve in
\texttt{anchors} (and consequently, \texttt{particles}), in order to maximize locality
preservation from the 3D simulation domain to the linear storage. To efficiently address
the cells, one extra layer encoding the locality preserving mapping has to be added, in
the form of the first vector \texttt{map}. To access a cell, the three indices $i_x$,
$i_y$, $i_z$ specifying its position in the grid are converted to a linear index $i$ (a
simple way is through the formula $i = i_z * N_y * N_x + i_y * N_x + i_x$, where $N_x$
$N_y$ $N_z$ is the number of cells along the $x$, $y$ and $z$ axis in the grid
respectively). The \texttt{map} vector serves as a lookup table, so that its $i$-th
element contains the pointer to that cell's representation on \texttt{anchors}. LP grid
advantages include cohesive storage, quick neighbour search and interaction scanning,
exploitation of the SPH algorithm access patterns and fast, in-place update.

@@

\begin{figure}[h!]
  \includegraphics[width=.33\textwidth]{figures/impulse-heatmap-0.png}
  \includegraphics[width=.32\textwidth]{figures/impulse-heatmap-1.png}
  \includegraphics[width=.33\textwidth]{figures/impulse-heatmap-2.png}
  \caption{Tsunami impulse heatmaps for three different urban models visualized under
    Paraview\textsuperscript{TM}. Most of the energy of the waves is absorbed by the first
    obstacle in their way.}
  \label{fig:impulse-heatmaps}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{figures/if-city0-free.png}
  \includegraphics[width=\textwidth]{figures/if-city0-seawall.png}
  \caption{Comparison between the impulse heatmap of a tsunami hit on the same urban
    coastline model, with (up) and without (down) the protection from a seawall. Seawalls
    are commonly found in high-risk areas, as they reduce impact effects significantly.}
  \label{fig:impulse-heatmaps-seawall}
\end{figure}

@@

\paragraph{} Although our framework provides rich and detailed data, a quantitative
comparison to either field measurements or results of other methods utilizing different
versions of the SPH formulations couldn't be reliably made. We haven't yet implemented a
way to configure the wave's initial conditions and coastline terrain to model the impact
according to predictions of large scale simulations or data from past
incidents. Qualitatively, our method seems to compare well to similar codes utilizing SPH
to simulate small scale tsunami interactions with coastline structures. Other methods
usually make use of SPH enhancements originating from the CFD literature, which aim to
improve some aspect of the flow (for example incompressibility, regarding WCSPH). In this
particular application domain though, boundary interactions can be arguably considered
more important than the flow itself. Our approach, enriching SPH with direct positional
constraint solving, shows promise as an efficient way for dealing explicitly and exactly
with momentum preservation and detailed fluid-structure impulse recording.

>>>>

\paragraph{} Simulations of natural phenomena are a precious tool for analysis and
understanding of the processes behind them as well as the implications of
those. Especially fluid dynamics is one of the fields most benefited by the explosive
growth of high performance parallel computing architectures of the last years. Tsunamis
are one of the most devastating natural disasters, with much attention drawn to them
lately, especially after the 2004 Indian Ocean tsunami and the 2011 T\={o}hoku earthquake
and tsunami, two of the largest incidents in modern history. Multiscale modelling of
tsunami generation, propagation and impact is a trending research area, as respective
simulations give valuable insights into the underlying mechanisms and relations between
the various stages of an unfolding tsunami incident, while also facilitating the
assessment of potential hazard it poses upon impact on a coastline.

@@

\paragraph{} Tsunami simulations have been shown to be a valuable tool in the literature,
aiding in estimation of key parameters of a tsunami incident, such as its propagation
course and coastal inundation. Simulations of the devastating 2004 Indian Ocean tsunami
have been carried out by Wang and Liu \cite{wang2007} and Ioualalen et
al. \cite{ioualalen2007}, using nonlinear shallow water equations and nonlinear Boussinesq
models respectively. In both cases, good agreement between calculations and field
measurements of inundation and runup indicate the robustness of these approches. Using two
different models, Kakinuma \cite{kakinuma2008} reproduced a past incident with sufficient
accuracy. The governing equations for both were the continuity and Reynolds equations for
incompressible fluids in porous media, while water surface displacement was determined by
the vertically integrated continuity equation for the first and the 3D Volume of Fluid
method for the second model. Lastly, Samaras et al. \cite{samaras2015} used a 2D
horizontal model based on the higher oder Boussinesq equations to simulate tsunami-induced
coastal inundation in two relevant areas of interest in the Mediterranean.

@@

\paragraph{} Due to its generality and adaptability, SPH has been the method of choice for
many applications and relative extensions. Macklin and M\"{u}ller
\cite{macklin2013position} enriched SPH with positional geometric constraints, thus
enforcing incompressibility while maintaining stability and allowing for large
timesteps. Rigid-fluid interaction is one of the strong aspects of the method, as is shown
by Akinci et al. \cite{akinci2012versatile}, where rigid surfaces are sampled by boundary
particles, which adaptively contribute to fluid properties to address boundary region
deficiencies and inhomogeneities, in order to incorporate rigid bodies to a unified
hydrodynamic framework. Finally, a thorough overview of various implementation algorithms
and data structures for SPH, together with their advantages and drawbacks is provided by
Dom\'{i}nguez et al. \cite{dominguez2011}.

@@

\paragraph{} Starting from the identity:
\begin{equation*}
  f(\vec{r}) = \int_Vf(\vec{x}) \delta(\vec{r} - \vec{x}) d\vec{x},
\end{equation*}
where $\delta(\vec{r})$ the Dirac delta function and $\vec{x} \in V$, one can obtain a
more general interpolation rule by substituting $\delta(\vec{r})$ with a smoothing kernel
$W(\vec{r}, h)$:
\begin{equation*}
  \label{eq:c-approx}
  f(\vec{r}) \approx \int_V f(\vec{x}) W(\vec{r}-\vec{x}, h) d\vec{x}
\end{equation*}
whose limit when $h\to0$ approaches the delta fucntion and is normalized to unity:
\begin{equation*}
  \label{eq:kernel-properties}
  \lim_{h\to0}W(\vec{r}, h) = \delta(\vec{r})\ \ \
  \text{and}\ \ \
  \int_VW(\vec{r}, h) d\vec{x} = 1
\end{equation*}
The smoothing radius $h$ serves as a cutoff radius in the smoothing process, as particles
beyond that distance have no contribution to the sum, i.e. $W(r,h) = 0$ when $r>h$. For
the discrete case, where $f$ is discretized to particles with density $\rho$ and mass $m$,
the weighting ratio $m/\rho$ can be used to construct a weighted sum interpolant for any
field $A$:
\begin{equation}
  \label{eq:d-approx}
  A(\vec{r}) = \sum_i \frac{m_i}{\rho_i} A(\vec{r}_i) W(\vec{r}-\vec{r}_i, h)
\end{equation}
which lies at the heart of the SPH formulation. According to this, the gradient can be
computed by the following approximation:
\begin{equation}
  \label{eq:d-grad}
  \nabla A(\vec{r}) = \sum_i \frac{m_i}{\rho_i} A(\vec{r}_i) \nabla W(\vec{r} - \vec{r}_i, h)
\end{equation}
The obvious advantage of this is the exclusive dependence on the smoothing kernel
gradient, which can be precomputed for sensible kernel choices. However, this formula can
lead to unsymmetric pair forces, compromising the conservation of linear and angular
momentum of the system. To symmetrize these forces depending on gradients (like those
originating from pressure differences), we can use the product rule:
\begin{equation*}
  \label{eq:grad-identity}
  \nabla \left( \frac{P}{\rho} \right) =
  \frac{\nabla P}{\rho}-
  \frac{P}{\rho^2} \nabla \rho
  \hspace{10pt} \Leftrightarrow \hspace{10pt}
  \nabla P = \rho \left[ \frac{P}{\rho^2} \nabla \rho + \nabla \left( \frac{P}{\rho}
    \right) \right]
\end{equation*}
to obtain an alternative approximation of gradient
\begin{align}
  \label{eq:grad-est}
  \nabla P & = \rho \left[ \frac{P}{\rho^2} \sum_i \frac{m_i}{\rho_i} \rho_i \nabla
             W(\vec{r}-\vec{r}_i, h)
             +
             \sum_i \frac{m_i}{\rho_i} \frac{P_i}{\rho_i} \nabla W(\vec{r}-\vec{r}_i, h)
             \right] \nonumber \\
           & = \rho \sum_i m_i \left(\frac{P}{\rho^2} + \frac{P_i}{\rho_i^2} \right)
             \nabla W(\vec{r}-\vec{r}_i, h)
\end{align}
which is antisymmetric for all interacting particle pairs. Viscosity forces on the other
hand are proportional to the laplacian of the velocity field:
\begin{equation}
  \label{eq:lapl-est}
  \nabla^2\vec{v} = \sum_i \frac{m_i}{\rho_i} (\vec{v}_i - \vec{v}) \nabla^2
  W(\vec{r}-\vec{r}_i, h)
\end{equation}
and are always antisymmetric, since they depend on velocity difference
$\vec{v}_i - \vec{v}$ between particles.  In each timestep of the simulation, the density
of all particles is first computed according to equation (\ref{eq:d-approx}):
\begin{equation}
  \label{eq:dens-est}
  \rho = \sum_i m_i W(\vec{r}-\vec{r}_i, h)
\end{equation}
as it depends only on the relative position of those. The pressure at each particle
location is then obtained from its respective density through an equation of state. After
this step, the pressure and viscosity forces are computed from the particle data and
integrated back into the position and velocity of the particles.

@@

\subsubsection{Simulation initialization} Each simulation under our implementation
consists of two elements, the coastline terrain (static) and the tsunami wave
(dynamic). For the simulation setup, terrain is imported from a suitable 3D geometry
definition file format, the initial conditions of the impacting wave (position and
velocity) are configured and the desired discretization resolution for the fluid (i.e. the
number of particles it is discretized into) is set. From these conditions, the terrain and
fluid are initialized and key parameters are computed as subsequently described. Terrain
geometry is uniformly scaled by a user-supplied factor and docked to the origin of
coordinates and the particle effective radius $r$ is determined such that the specified
discretization resolution is achieved. Fluid particles are initially placed on a Hexagonal
Close-Packed lattice covering the fluid initial position, in order to accomplish the
densest possible packing and symmetry:
\begin{equation}
  \label{eq:hcp}
  [x, y, z] = \left[ 2i+[(j+k) \bmod 2], \sqrt{3}[j + \frac{1}{3} (k \bmod 2)],
    \frac{2\sqrt{6}}{3} k \right] r
\end{equation}
In this configuration, the smoothing radius $h$ is computed such that each particle has
approximately 50 neighbours (following the empirical rule established in the
literature). The timestep is calculated according to the Courant-Friedrichs-Lewy
criterion:
\begin{equation}
  \label{eq:cfl}
  \delta t_{\text{CFL}} = C \frac {\delta x}{v_{\text{max}}},
\end{equation}
for values of Courant number $C\approx0.5$ with characteristic length $\delta x$ equal to
the particle effective radius and maximum velocity $v_{\text{max}}$ determined by the
maximum mechanical energy in the initial configuration.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{../report/figures/lp-grid.pdf}
  \caption{Organization of the custom data structure designed for the efficient storing
    and interaction scanning between simulation particles. From top to bottom,
    \texttt{map} encodes the 3D to linear locality preserving mapping onto
    \texttt{anchors}, which in turn points to each cell's particles in
    \texttt{particles}.}
  \label{fig:lp-grid}
\end{figure}

\subsubsection{Data organization and export} Rigid body dynamics are handled by the Bullet
physics engine. A custom cell list data structure (LP grid) was implemented in order to
optimize particle dynamic storage and access time. The simulation domain is divided by a
regular 3D grid of spacing equal to the smoothing radius into cubic cells containing the
fluid particles. Particles are generated as Bullet objects and are stored in the LP grid,
which consists of three storage vectors. As shown in Figure \ref{fig:lp-grid}, particles
are accessed by following pointers through those vectors in order. The \texttt{map} vector
contains pointers to \texttt{anchors} and in turn \texttt{anchors} pointers to
\texttt{particles}, which contains the simulation particles. Each cell's particles are
continuously stored in the \texttt{particles} vector. Each element of \texttt{anchors}
represents a cell and contains a pointer to the start of the region that contains that
cell's particles in \texttt{particles}. Since SPH access patterns are heavily reliant on
neighbour searching, increasing the locality in the linear order in which cells are stored
is clearly beneficial to performance, due to better utilization of cache memory. For that
reason, cells are represented spatially sorted along a space-filling curve in
\texttt{anchors} (and consequently, \texttt{particles}), in order to maximize locality
preservation from the 3D simulation domain to the linear storage. To efficiently address
the cells, one extra layer encoding the locality preserving mapping has to be added, in
the form of the first vector \texttt{map}. To access a cell, the three indices $i_x$,
$i_y$, $i_z$ specifying its position in the grid are converted to a linear index $i$ (a
simple way is through the formula $i = i_z * N_y * N_x + i_y * N_x + i_x$, where $N_x$
$N_y$ $N_z$ is the number of cells along the $x$, $y$ and $z$ axis in the grid
respectively). The \texttt{map} vector serves as a lookup table, so that its $i$-th
element contains a pointer to that cell's representation on \texttt{anchors}. LP grid
advantages include cohesive storage, quick neighbour search and interaction scanning,
exploitation of the SPH algorithm access patterns and fast, in-place update.

@@

\begin{figure}[h!]
  \includegraphics[width=.33\textwidth]{figures/impulse-heatmap-0.png}
  \includegraphics[width=.32\textwidth]{figures/impulse-heatmap-1.png}
  \includegraphics[width=.33\textwidth]{figures/impulse-heatmap-2.png}
  \caption{Tsunami impulse heatmaps for three different urban models visualized under
    Paraview\textsuperscript{TM}. Most of the wave's energy is absorbed by the first
    obstacle in its way.}
  \label{fig:impulse-heatmaps}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{figures/if-city0-free.png}
  \includegraphics[width=\textwidth]{figures/if-city0-seawall.png}
  \caption{Comparison between the impulse heatmap of a tsunami hit on the same urban
    coastline model, without (top) and with (bottom) the protection of a seawall. Seawalls
    are commonly found in high-risk areas, as they reduce impact effects significantly.}
  \label{fig:impulse-heatmaps-seawall}
\end{figure}

@@

\paragraph{} Although our framework provides rich and detailed data, a quantitative
comparison to either field measurements or results of other methods utilizing different
versions of the SPH formulation couldn't be reliably made. We haven't yet implemented a
way to configure the wave's initial conditions and coastline terrain to model the impact
according to predictions of large scale simulations or data from past
incidents. Qualitatively, our method seems to compare well to similar codes utilizing SPH
to simulate small scale tsunami interactions with coastline structures. Other methods
usually make use of SPH enhancements originating from the CFD literature, which aim to
improve some aspect of the flow (for example incompressibility, regarding WCSPH). In this
particular application domain though, boundary interactions can be arguably considered
more important than the flow itself. Our approach, enriching SPH with direct positional
constraint solving, shows promise as an efficient way for dealing explicitly and exactly
with momentum preservation and detailed fluid-structure impulse recording.
